---
title: "Boston Housing Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Boston Housing Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To begin, load the `interpretnn` package.

```{r setup}
library(interpretnn)
```

Also, load the package that we will use to fit the neural network.
Our package works with a number of popular R packages for neural networks, and
here we will use the `nnet` package.


```{r, message=FALSE, warning=FALSE}
library(nnet)
```

Now, load the data.

```{r}
# load data ---------------------------------------------------------------
data(Boston)
```


Next, we fit a neural network.
We will fit a neural network on the respose variable, `medv`, using all covariates and with two hidden nodes. 
As neural networks require random initial weights to begin learning, we use
`set.seed()` for reproducibility.

```{r}
set.seed(100)
nn <- nnet(medv ~ ., data = Boston, size = 2, trace = FALSE,
           linout = TRUE, maxit = 1000)
```

We can then create a `interpretnn` object

```{r intnn, cache = TRUE}
intnn <- interpretnn(nn, X = Boston[, -ncol(Boston)]) 
```

A useful summary table can then be produced using the `summary()` function

```{r}
summary(intnn)
```

This tells provides us with simple point estimates of the effects, and
the results from the multiple-parameter Wald test for each input.

We can visualise the covariate effects and their associated uncertainty using
the `plot()` function, which creates Partial Covariate Effect (PCE) plots.

<!-- ```{r, cache = TRUE} -->
<!-- plot(intnn, conf_int = TRUE) -->
<!-- ``` -->

There is also a `plotnn()` function that visualise the significance of each weight
from the single-parameter Wald test.


```{r}
plotnn(intnn)
```

